### 2023-06-15 write-ups/cogsci23_poster/document.tex
work on poster

				{\LARGE\textbf{Communicative reduction in referring expressions \\ within a
						multi-player negotiation game}}\\
				{\Large Veronica Boyce, Michael C. Frank} \\
				{Stanford University, send correspondence to vboyce@mit.edu}

@@

	\begin{textblock}{.32}(0,0.16)
		\begin{tcolorbox}[title= {\centering Goals }]
			\begin{small}\centering
				\bigskip
			The ability to form novel conventions is a key signature of efficient
			linguistic communication.
 In dyadic reference games, we commonly observe 
 \begin{itemize}
 	\item \textbf{reduction} as utterances shorter over time,
 	 \item \textbf{convergence} within groups to a shared nick name,
 	  \item \textbf{divergence} between groups as each focuses on different features.
   \end{itemize}  CITATIONS

Do these phenomena occur in strategic games with more complex goals?

@@

	\begin{textblock}{.32}[0,1](0,1 )
		\begin{tcolorbox}[title={\centering Experimental design }]

@@

			\begin{small}
				 During selection (A) each participant sees 6 flowers, 4 with value bars. Players can use a chat box to communicate before making selections. Then they see feedback (B) indicating who chose what.  When multiple players select the same flower, they recieve a lower value rather than what is shown.

				In \emph{individual utility} games (18 games), each player earned points for the
				flowers they selected; in the \emph{shared utility} games (21 games), the points
				were averaged together, and all players in a game got the same reward.
								Each group plays 24 trials with images drawn from a set of 12 flowers. This data was first presented in  Mankewitz et al. (2021).

								We measure distance between two utterances by the cosine of the angle between their embedings using SBERT (CITATION).

@@

@@

	\begin{textblock}{.41}[0,0](.33,.16)
	\begin{tcolorbox}[title={\centering Referring expressions reduce over time}]  
		\includegraphics[width=.95\textwidth]{wordcount-1.pdf}

	\begin{small}	Over time individual utterances shorten, but the same number of referring expressions are produced.     \end{small}                                              
	\end{tcolorbox}
\end{textblock}

		\begin{textblock}{.41}[0,0](.33,.43)

		\begin{tcolorbox}[title={\centering Expressions converge within groups}]  
			\includegraphics[width=.95\textwidth]{during-1.pdf}                            			                                                  
			\begin{small}

				Descriptions to the same flower in nearby trials increase in similarity with a group.

				Similarity decreases slightly for the same flower across games.

				Flower names become more distinctive as descriptions for two different flowers become less similar.

	\begin{textblock}{.41}[0,1](.33,1)
	\begin{tcolorbox}[title={ \centering 					Incentive conditions differed a bit}]  
		\begin{minipage}{.45\textwidth}
			\includegraphics[width=\textwidth]{withinend-1.pdf}    
		\end{minipage}
	\hfill
	\noindent
	\begin{minipage}{.45\textwidth}
				\begin{small}

				Individual and shared utilities conditions differed slightly in divergence rate during games (above). In post-game descriptions (left), shared utility games show greater cross-game similarity for the same flowers than individual utility.

				\end{small}
	\end{minipage}

@@

		\begin{textblock}{.25}[1,0](1,.16)
	\begin{tcolorbox}[title={\centering Examples}]

		\centering
		\begin{footnotesize}
			Descriptions of different flowers from different games, illustrating reduction and convergence phenomenon. Images from experimental design: flower 1 upper left, flower 2 lower center, flower 3 lower left.
			\vspace{-1em}

			\vspace{2em}
			Cosine similarities between pairs of descriptions.

			\vspace{-1em}
			\begin{tabular}[t]{>{\raggedright\arraybackslash}p{9em}>{\raggedright\arraybackslash}p{9em}r}
				\toprule
				Expression 1 & Expression 2 & Sim\\
				\midrule
				the red center & red middle & 0.78\\
				droopy iris flower & multi flowers & 0.56\\
				droopy iris flower & droopy & 0.56\\
				cluster & bundle & 0.25\\
				red middle & black background & 0.25\\
				droopy iris flower & the red center & 0.09\\
				droopy & bundle & 0.03\\
				\bottomrule
			\end{tabular}
		\end{footnotesize}

	\end{tcolorbox}
\end{textblock}
	\begin{textblock}{.25}[1,1](1,1)
		\begin{tcolorbox}[title= {\centering Conclusion}]
			\begin{small} Reduction and convergence patterns generalize to freer-form and
			more naturalistic domain of a negotiation game
			\end{small}
			\begin{scriptsize}

				\textbf{References: }\noindent
				TODO
			\end{scriptsize}
\end{tcolorbox}
\end{textblock}

>>>>

				{\LARGE\textbf{Communicative reduction in referring expressions \\ within a
						multi-player negotiation game}}\\
				{\Large Veronica Boyce, Michael C. Frank} \\
				{Stanford University, contact: vboyce@stanford.edu}

@@

	\begin{textblock}{.32}(0,0.15)
		\begin{tcolorbox}[title= {\centering Goals }]
			\vspace{.5em}
			\begin{small}\centering
				\bigskip
			\textbf{The ability to form novel conventions is a key signature of efficient
			linguistic communication.}

			\vspace{.5em}
 In dyadic reference games (Clark \& Wilkes-Gibbs 1986, Hawkins et al. 2020), speaker-listener pairs show the following patterns:
 \begin{itemize}
 	\item \textbf{reduction} as utterances shorter over time,
 	 \item \textbf{convergence} within groups to a shared nickname,
 	  \item \textbf{divergence} between groups as different nicknames develop.
   \end{itemize}

\vspace{.5em}
\textbf{Do these patterns occur for reference expressions in strategic games with more complex goals?}
\vspace{.5em}

@@

	\begin{textblock}{.32}[0,1](0,1 )
		\begin{tcolorbox}[title={\centering Experimental design }]
\vspace{.5em}

@@

			\vspace{.5em}
			\begin{small}

				Participants were assigned to 3-player games. 
				 During selection (A) each participant saw 6 flowers, 4 with value bars. Players could communicate in a chat box before each selecting a flower. Then they saw feedback (B) indicating who chose what.  When multiple players selected the same flower, they received a lower value rather than the indicated value.

\vspace{.5em}

				In \emph{individual utility} games (18 games), each player earned points for the
				flowers they selected; in the \emph{shared utility} games (21 games), the points
				were averaged together, and all players in a game got the same reward.
								Each group played 24 trials with images drawn from a set of 12 flowers. This data was first presented in  Mankewitz et al. (2021).

@@

		\vspace{.5em}
		\end{tcolorbox}
	\end{textblock}

	\begin{textblock}{.41}[0,0](.33,.15)
	\begin{tcolorbox}[title={\centering Referring expressions reduced over time}]  
		\vspace{.5em}
		\centering
		\includegraphics[width=.9\textwidth]{wordcount-1.pdf}

	\begin{small}	Descriptions got shorter over time, but the number of descriptions stayed constant.   \end{small}                                              
	\end{tcolorbox}
\end{textblock}

		\begin{textblock}{.41}[0,0](.33,.4)

		\begin{tcolorbox}[title={\centering Referring expressions converged within groups}]  
			\vspace{.5em}
			\centering
			\includegraphics[width=.9\textwidth]{during-1.pdf}                            			                                                  
			\begin{small}

					Similarity between two descriptions was measured by the cosine between their S-BERT embeddings (Reimers \& Gurevych, 2019).
				\begin{itemize}

				\item Similarity increased for the same flower within games (top left, center).

				\item Similarity decreased slightly for the same flower across games (top right).

				\item Descriptions for different flowers became more distinct (bottom).
				\end{itemize}
			\end{small}
		\vspace{.5em}
		\end{tcolorbox}
	\end{textblock}

	\begin{textblock}{.41}[0,1](.33,1)
	\begin{tcolorbox}[title={ \centering 					Shared utilities games diverged less}]  
		\begin{minipage}{.4\textwidth}
			\vspace{.5em}
			\includegraphics[width=\textwidth]{withinend-1.pdf}    
		\end{minipage}
	\hfill
	\noindent
	\begin{minipage}{.55\textwidth}
				\begin{small}
					\vspace{.5em}
			Shared utility games diverged less from each other in how to refer to each flower, both during game (above, top right) and in post-game descriptions (left), possibly due to the shared utilities encouraging coordination and thus comprehension.

				\vspace{.2em}
				\end{small}

	\end{minipage}

@@

		\begin{textblock}{.25}[1,0](1,.15)
	\begin{tcolorbox}[title={\centering Examples}]
		\vspace{.2em}

		\centering
		\begin{footnotesize}
			Descriptions of different flowers from different games. Images shown in  experimental design: flower 1 upper left, flower 2 lower center, flower 3 lower left.
			\vspace{-1em}

			\vspace{1em}
			Cosine similarities between pairs of descriptions.

			\vspace{-1.5em}
			\begin{tabular}[t]{>{\raggedright\arraybackslash}p{9em}>{\raggedright\arraybackslash}p{9em}r}
				\toprule
				Expression 1 & Expression 2 & Sim\\
				\midrule
				the red center & red middle & 0.78\\
				droopy iris flower & multi flowers & 0.56\\
				droopy iris flower & droopy & 0.56\\
				cluster & bundle & 0.25\\
				red middle & black background & 0.25\\
				droopy iris flower & the red center & 0.09\\
				droopy & bundle & 0.03\\
				\bottomrule
			\end{tabular}
		\end{footnotesize}
		\vspace{.5em}
	\end{tcolorbox}
\end{textblock}
	\begin{textblock}{.25}[1,1](1,1)
		\begin{tcolorbox}[title= {\centering Conclusion}]
			\vspace{.5em}

			\begin{small}

				 Reduction and 
				and conventionalization occur even in strategic games with more open-ended negotiation and more complex goals than reference games.

		\vspace{.5em}
		\begin{tiny}
			References: Clark, H., \& Wilkes-Gibbs, D. (1986). Referring as a collaborative
			process. $\bullet$
			Reimers, N., \& Gurevych, I. (2019). Sentence-{BERT}:
				{Sentence Embeddings} using {Siamese BERT-Networks}. $\bullet$ 
Hawkins, R., Frank, M., \& Goodman, N. (2020). Characterizing
			the dynamics of learning in repeated reference games. $\bullet$
		Mankewitz, J., et al. (2021). Multi-party referential communication in
	complex strategic games.

			\end{tiny}

@@
